---
title: "Communitystructure"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
library(readxl)
library(tidyverse)
library(ggplot2)
library(rcompanion) 
library(ggpubr)
library(dplyr)
library(car)
library(e1071)
library(afex)
```

#interactive effects of time,clusterness with a nested random effect of nodes and grid on shannon's diversity
```{r setup, include=TRUE}
SDM<-lmer(SD~TimePoint*Clusterness+(1|Grid/Location),data = DSD)
summary(SDM)
anova(SDM)
plot(SDM)
shapiro.test(resid(SDM))
```



#data transform does not meet the standard for normal distribution
```{r,echo=FALSE}
#Transform the data 
DSD$SD_T= transformTukey(DSD$SD,plotit = FALSE)
```


#using afex package to model
```{r }
SDM_AC<-mixed(SD~TimePoint*Clusterness+(1|Grid/Location),data = DSD,method="PB",check.contrasts=FALSE,args.test = list(nsim = 2000))
summary(SDM_AC)
```




#using afex package to model
```{r }
SDM_AD<-mixed(SD~TimePoint*Distance+(1|Grid/Location),data = DSD,method="PB",check.contrasts=FALSE,args.test = list(nsim = 2000))
summary(SDM_AD)
```

```{r }
DSD$Grid<- factor(DSD$Grid,levels = unique(DSD$Grid))
ggplot( DSD,aes(x=TimePoint,y=SD,color=Clusterness))+
  geom_point()+
labs(title="Shannon's diversity change across time")+
  facet_wrap(~Grid,nrow=2)+
  theme_classic()
```


```{r }
DSD$Grid<- factor(DSD$Grid,levels = unique(DSD$Grid))
ggplot( DSD,aes(x=Distance,y=SD,color=Clusterness))+
  geom_point()+
labs(title="Shannon's diversity change across distance")+
  facet_wrap(~Grid,nrow=2)+
  theme_classic()
```


#SHANNON'S DIVERSITY PER GRID ALONG TIME

#lmPerm: Exact argument for evaluate all permutations
```{r }
G0_6<- subset(SD, TimePoint!="1"&Clusterness=="0.6")
summary(lmp(SD~TimePoint,data = G0_6))
```



```{r }
SD06<- aov(SD~TimePoint,data = G0_6)
summary(SD06)
ggline( G0_6,x= "TimePoint",y= "SD",
       add= c("mean_se","jitter"),point.color = "blue",
       ylab = "Shannon's diversity",xlab= "Timepoint")
```


```{r }
G0_72<- subset(COM1, TimePoint!="1"&Clusterness=="0.72")
summary(lmp(SD~TimePoint,data = G0_72))
```


```{r }

SD072<- aov(SD~TimePoint,data = G0_72)
summary(SD072)
ggline( G0_72,x= "TimePoint",y= "SD",
       add= c("mean_se","jitter"),point.color = "blue",
       ylab = "Shannon's diversity",xlab= "Timepoint")
```




```{r}
G0_77<- subset(COM1, TimePoint!="1"&Clusterness=="0.6")
summary(lmp(SD~TimePoint,data = G0_77))
```



```{r }

SD077<- aov(SD~TimePoint,data = G0_77)
summary(SD077)
ggline( G0_77,x= "TimePoint",y= "SD",
       add= c("mean_se","jitter"),point.color = "blue",
       ylab = "Shannon's diversity",xlab= "Timepoint")
```

```{r setup, include=TRUE}
G0_86<- subset(COM1, TimePoint!="1"&Clusterness=="0.86")
summary(lmp(SD~TimePoint,data = G0_86))
```



```{r setup, include=TRUE}

SD086<- aov(SD~TimePoint,data = G0_86)
summary(SD086)
ggline( G0_86,x= "TimePoint",y= "SD",
       add= c("mean_se","jitter"),point.color = "blue",
       ylab = "Shannon's diversity",xlab= "Timepoint")
```


```{r setup, include=TRUE}
G0_92<- subset(COM1, TimePoint!="1"&Clusterness=="0.92")
summary(lmp(SD~TimePoint,data = G0_92))
```


```{r setup, include=TRUE}

SD092<- aov(SD~TimePoint,data = G0_92)
summary(SD092)
ggline( G0_92,x= "TimePoint",y= "SD",
       add= c("mean_se","jitter"),point.color = "blue",
       ylab = "Shannon's diversity",xlab= "Timepoint")
```

```{r setup, include=TRUE}
G1_02<- subset(COM1, TimePoint!="1"&Clusterness=="0.6")
summary(lmp(SD~TimePoint,data = G1_02))
```

```{r setup, include=TRUE}

SD102<- aov(SD~TimePoint,data = G1_02)
summary(SD102)
ggline( G1_02,x= "TimePoint",y= "SD",
       add= c("mean_se","jitter"),point.color = "blue",
       ylab = "Shannon's diversity",xlab= "Timepoint")
```

```{r setup, include=TRUE}

lm(SD~TimePoint,G1_02)

plot(SD~TimePoint,G1_02)+
  abline(-0.0385,0.03024)

```

```{r setup, include=TRUE}
G1_09<- subset(COM1, TimePoint!="1"&Clusterness=="1.09")
summary(lmp(SD~TimePoint,data = G1_09))
```


```{r setup, include=TRUE}

SD109<- aov(SD~TimePoint,data = G1_09)
summary(SD109)
ggline( G1_09,x= "TimePoint",y= "SD",
       add= c("mean_se","jitter"),point.color = "blue",
       ylab = "Shannon's diversity",xlab= "Timepoint")
```



```{r setup, include=TRUE}
G1_13<- subset(COM1, TimePoint!="1"&Clusterness=="1.13")
summary(lmp(SD~TimePoint,data = G1_13))
```


```{r setup, include=TRUE}

SD113<- aov(SD~TimePoint,data = G1_13)
summary(SD113)
ggline( G1_13,x= "TimePoint",y= "SD",
       add= c("mean_se","jitter"),point.color = "blue",
       ylab = "Shannon's diversity",xlab= "Timepoint")
```


```{r setup, include=TRUE}
G1_18<- subset(COM1, TimePoint!="1"&Clusterness=="1.18")
summary(lmp(SD~TimePoint,data = G1_18))
```


```{r setup, include=TRUE}

SD118<- aov(SD~TimePoint,data = G1_18)
summary(SD118)
ggline( G1_18,x= "TimePoint",y= "SD",
       add= c("mean_se","jitter"),point.color = "blue",
       ylab = "Shannon's diversity",xlab= "Timepoint")
```


```{r setup, include=TRUE}
G1_29<- subset(COM1,TimePoint!="1"&Clusterness=="1.29")
summary(lmp(SD~TimePoint,data = G1_29))
```


```{r setup, include=TRUE}

SD129<- aov(SD~TimePoint,data = G1_29)
summary(SD129)
ggline( G1_29,x= "TimePoint",y= "SD",
       add= c("mean_se","jitter"),point.color = "blue",
       ylab = "Shannon's diversity",xlab= "Timepoint")
```


#linear regression of shannon's diversity for each grid over time: correlation

#pearson correlation Grid0.6=0.3369;0.1287(include TP1)
```{r setup, include=TRUE}
scatter.smooth(x=G0_6$TimePoint,y=G0_6$SD,main="G0.6Diversity~Time")

plot(density(G0_6$TimePoint),main="Density Plot: Timepoint", ylab="Frequency", sub=paste("Skewness:", round(e1071::skewness(G0_6$TimePoint), 2)))
plot(density(G0_6$SD),main="Density Plot: SD", ylab="Frequency", sub=paste("Skewness:", round(e1071::skewness(G0_6$SD), 2)))

cor(G0_6$TimePoint,G0_6$SD)
```


##pearson correlation Grid0.72=0.6337;0.4282(include TP1)
```{r setup, include=TRUE}
scatter.smooth(x=G0_72$TimePoint,y=G0_72$SD,main="G0.72Diversity~Time")

plot(density(G0_72$SD),main="Density Plot: SD", ylab="Frequency", sub=paste("Skewness:", round(e1071::skewness(G0_72$SD), 2)))

cor(G0_72$TimePoint,G0_72$SD)


```


#pearson correlation Grid0.77=0.625;0.44789(include TP1)
```{r setup, include=TRUE}
scatter.smooth(x=G0_77$TimePoint,y=G0_77$SD,main="G0.77Diversity~Time")

plot(density(G0_77$SD),main="Density Plot: SD", ylab="Frequency", sub=paste("Skewness:", round(e1071::skewness(G0_77$SD), 2)))

cor(G0_77$TimePoint,G0_77$SD)
```


#pearson correlation Grid0.86=0.389;0.0787(TP1 included)
```{r setup, include=TRUE}
scatter.smooth(x=G0_86$TimePoint,y=G0_86$SD,main="G0.86Diversity~Time")
cor(G0_86$TimePoint,G0_86$SD)
```



#pearson correlation Grid0.92=0.56???0.4(TP1 included)
```{r setup, include=TRUE}
scatter.smooth(x=G0_92$TimePoint,y=G0_92$SD,main="G0.92Diversity~Time")
cor(G0_92$TimePoint,G0_92$SD)
```


#pearson correlation Grid1.02=0.7428???0.504(TP1 included)
```{r setup, include=TRUE}
scatter.smooth(x=G1_02$TimePoint,y=G1_02$SD,main="G1.02Diversity~Time")
cor(G1_02$TimePoint,G1_02$SD)
```


#pearson correlation Grid1.09=0.654???0.4708
```{r setup, include=TRUE}
scatter.smooth(x=G1_09$TimePoint,y=G1_09$SD,main="G1.09Diversity~Time")
cor(G1_09$TimePoint,G1_09$SD)
```


#pearson correlation Grid1.13=0.619???0.2945
```{r setup, include=TRUE}
scatter.smooth(x=G1_13$TimePoint,y=G1_13$SD,main="G1.13Diversity~Time")
cor(G1_13$TimePoint,G1_13$SD)
```


#pearson correlation Grid1.18=0.4289???0.202
```{r setup, include=TRUE}
scatter.smooth(x=G1_18$TimePoint,y=G1_18$SD,main="G1.18Diversity~Time")
cor(G1_18$TimePoint,G1_18$SD)
```


#pearson correlation Grid1.=0.349???0.1789
```{r setup, echo=TRUE}
scatter.smooth(x=G1_29$TimePoint,y=G1_29$SD,main="G1.29Diversity~Time")
cor(G1_29$TimePoint,G1_29$SD)
```



#Correaltion between diversity and time in each grid
```{r setup, include=TRUE}
ggplot(COR,aes(x=Grid,y=CorDT))+geom_point()+
  theme_classic()+
  labs(title="Coorelation value between shannon's diversity and time(no TP1) in each grid")
```


```{r setup, include=TRUE}
ggplot(COR,aes(x=Grid,y=CorDT1))+geom_point()+
  theme_classic()+
  labs(title="Coorelation value between shannon's diversity and time in each grid")
```




#SHANNON'S DIVERSITY PER TIME ALONG GRIDS

#lmPerm: Exact argument for evaluate all permutations
```{r setup, include=TRUE}
T2<- subset(COM1, TimePoint=="2")
summary(lmp(SD~Clusterness+(1|Grid),data = T2))
```



```{r setup, include=TRUE}


SDt2<- aov(SD~Grid,data = T2)
summary(SDt2)
ggline( T2,x= "Grid",y= "SD",
       add= c("mean_se","jitter"),point.color = "blue",
       ylab = "Shannon's diversity",xlab= "Grid")
```





```{r setup, include=TRUE}
T3<- subset(COM1, TimePoint=="3")
summary(lmp(SD~Clusterness+(1|Grid),data = T3))
```

```{r setup, include=TRUE}


SDt3<- aov(SD~Grid,data = T3)
summary(SDt3)
ggline( T3,x= "Grid",y= "SD",
       add= c("mean_se","jitter"),
       ylab = "Shannon's diversity",xlab= "Grid")
```

```{r setup, include=TRUE}
T4<- subset(COM1, TimePoint=="4")
summary(lmp(SD~Clusterness+(1|Grid),data = T4))
```

```{r setup, include=TRUE}

lm(SD~Clusterness,T4)

plot(SD~Clusterness,T4)+
  abline(0.18523,-0.09978)

```

```{r setup, include=TRUE}
T5<- subset(COM1, TimePoint=="5")
summary(lmp(SD~Clusterness+(1|Grid),data = T5))
```

```{r setup, include=TRUE}


SDt5<- aov(SD~Grid,data = T5)
summary(SDt5)
ggline( T5,x= "Grid",y= "SD",
       add= c("mean_se","jitter"),
       ylab = "Shannon's diversity",xlab= "Grid")
```

```{r setup, include=TRUE}
T6<- subset(COM1, TimePoint=="6")
summary(lmp(SD~Clusterness+(1|Grid),data = T6))
```



```{r setup, include=TRUE}


SDt6<- aov(SD~Grid,data = T6)
summary(SDt6)
ggline( T6,x= "Grid",y= "SD",
       add= c("mean_se","jitter"),
       ylab = "Shannon's diversity",xlab= "Grid")
```


```{r setup, include=TRUE}
T7<- subset(COM1, TimePoint=="7")
summary(lmp(SD~Clusterness+(1|Grid),data = T7))
```




```{r setup, include=TRUE}


SDt7<- aov(SD~Grid,data = T7)
summary(SDt7)
ggline( T7,x= "Grid",y= "SD",
       add= c("mean_se","jitter"),
       ylab = "Shannon's diversity",xlab= "Grid")
```



##pearson correlation between diversity and grid at TP2: 0.05406
```{r setup, include=TRUE}
TP2<- subset(COM1, TimePoint=="2")
scatter.smooth(x=TP2$Grid,y=TP2$SD,main="Diversity~Grid")

plot(density(TP2$SD),main="Density Plot: SD", ylab="Frequency", sub=paste("Skewness:", round(e1071::skewness(G0_72$SD), 2)))

cor(TP2$Grid,TP2$SD)

```

##pearson correlation between diversity and grid at TP3: -0.02611
```{r setup, include=TRUE}
TP3<- subset(COM1, TimePoint=="3")
scatter.smooth(x=TP3$Grid,y=TP3$SD,main="Diversity~Grid")

plot(density(TP3$SD),main="Density Plot: SD", ylab="Frequency", sub=paste("Skewness:", round(e1071::skewness(G0_72$SD), 2)))

cor(TP3$Grid,TP3$SD)

```

##pearson correlation between diversity and grid at TP4: -0.2172
```{r setup, include=TRUE}
TP4<- subset(COM1, TimePoint=="4")
scatter.smooth(x=TP4$Grid,y=TP4$SD,main="Diversity~Grid")

plot(density(TP4$SD),main="Density Plot: SD", ylab="Frequency", sub=paste("Skewness:", round(e1071::skewness(G0_72$SD), 2)))

cor(TP4$Grid,TP4$SD)
```
##pearson correlation between diversity and grid at TP5: -0.15049
```{r setup, include=TRUE}
TP5<- subset(COM1, TimePoint=="5")
scatter.smooth(x=TP5$Grid,y=TP5$SD,main="Diversity~Grid")

plot(density(TP5$SD),main="Density Plot: SD", ylab="Frequency", sub=paste("Skewness:", round(e1071::skewness(G0_72$SD), 2)))

cor(TP5$Grid,TP5$SD)
```

##pearson correlation between diversity and grid at TP6: -0.04443
```{r setup, include=TRUE}
TP6<- subset(COM1, TimePoint=="6")
scatter.smooth(x=TP6$Grid,y=TP6$SD,main="Diversity~Grid")

plot(density(TP6$SD),main="Density Plot: SD", ylab="Frequency", sub=paste("Skewness:", round(e1071::skewness(G0_72$SD), 2)))

cor(TP6$Grid,TP6$SD)
```
##pearson correlation between diversity and grid at TP7: 0.04225
```{r setup, include=TRUE}
TP7<- subset(COM1, TimePoint=="7")
scatter.smooth(x=TP7$Grid,y=TP7$SD,main="Diversity~Grid")

plot(density(TP7$SD),main="Density Plot: SD", ylab="Frequency", sub=paste("Skewness:", round(e1071::skewness(G0_72$SD), 2)))

cor(TP7$Grid,TP7$SD)
```
```{r setup, include=TRUE}
ggplot(CORDT,aes(x=TimePoint,y=corDG))+geom_point()+
  theme_classic()+
  labs(title="Coorelation value between shannon's diversity and Grid at each timepoint")
```


#SHANNON'S DIVERSITY PER GRID ALONG DISTANCE

#lmPerm: Exact argument for evaluate all permutations
```{r setup, include=TRUE}
G1<- subset(COM1, Clusterness=="0.6"&TimePoint!="1")
summary(lmp(SD~Distance+(1|Grid),data = G1))
```


```{r setup, include=TRUE}
G0_6<- subset(COM1, TimePoint!="1"&Clusterness=="0.6")

SD06D<- aov(SD~Distance,data = G0_6)
summary(SD06D)
ggline( G0_6,x= "Distance",y= "SD",
       add= c("mean_se","jitter"),point.color = "blue",
       ylab = "Shannon's diversity",xlab= "Distance from the central node")
```


```{r setup, include=TRUE}
G2<- subset(COM1, Clusterness=="0.72"&TimePoint!="1")
summary(lmp(SD~Distance+(1|Grid),data = G2))
```

```{r setup, include=TRUE}
G0_72<- subset(COM1,TimePoint!="1"&Clusterness=="0.72")

SD072D<- aov(SD~Distance,data = G0_72)
summary(SD072D)
ggline( G0_72,x= "Distance",y= "SD",
       add= c("mean_se","jitter"),point.color = "blue",
       ylab = "Shannon's diversity",xlab= "Distance from the central node")
```




```{r setup, include=TRUE}
G3<- subset(COM1, TimePoint!="1"&Clusterness=="0.77")
summary(lmp(SD~Distance+(1|Grid),data = G3))
```




```{r setup, include=TRUE}
G0_77<- subset(COM,TimePoint!="1"&Grid=="G0.77")

SD077D<- aov(SD~Distance,data = G0_77)
summary(SD077D)
ggline( G0_77,x= "Distance",y= "SD",
       add= c("mean_se","jitter"),point.color = "blue",
       ylab = "Shannon's diversity",xlab= "Distance from the central node")
```




```{r setup, include=TRUE}
G4<- subset(COM1, TimePoint!="1"&Clusterness=="0.86")
summary(lmp(SD~Distance+(1|Grid),data = G4))
```




```{r setup, include=TRUE}
G0_86<- subset(COM, TimePoint!="1"&Grid=="G0.86")

SD086D<- aov(SD~Distance,data = G0_86)
summary(SD086D)
ggline( G0_86,x= "Distance",y= "SD",
       add= c("mean_se","jitter"),point.color = "blue",
       ylab = "Shannon's diversity",xlab= "Distance from the central node")
```


```{r setup, include=TRUE}
G5<- subset(COM1, TimePoint!="1"&Clusterness=="0.92")
summary(lmp(SD~Distance+(1|Grid),data = G5))
```




```{r setup, include=TRUE}
G0_92<- subset(COM, TimePoint!="1"&Grid=="G0.92")

SD092D<- aov(SD~Distance,data = G0_92)
summary(SD092D)
ggline( G0_92,x= "Distance",y= "SD",
       add= c("mean_se","jitter"),point.color = "blue",
       ylab = "Shannon's diversity",xlab= "Distance from the central node")
```

```{r setup, include=TRUE}
G6<- subset(COM1, TimePoint!="1"&Clusterness=="1.02")
summary(lmp(SD~Distance+(1|Grid),data = G6))
```




```{r setup, include=TRUE}
G1_02<- subset(COM, TimePoint!="1"&Grid=="G1.02")
SD102D<- aov(SD~Distance,data = G1_02)
summary(SD102D)
ggline( G1_02,x= "Distance",y= "SD",
       add= c("mean_se","jitter"),
       ylab = "Shannon's diversity",xlab= "Distance from the central node")
```


```{r setup, include=TRUE}
G7<- subset(COM1, TimePoint!="1"&Clusterness=="1.09")
summary(lmp(SD~Distance+(1|Grid),data = G7))
```

```{r setup, include=TRUE}
G1_09<- subset(COM, TimePoint!="1"&Grid=="G1.09")
SD109D<- aov(SD~Distance,data = G1_09)
summary(SD109D)
ggline( G1_09,x= "Distance",y= "SD",
       add= c("mean_se","jitter"),
       ylab = "Shannon's diversity",xlab= "Distance from the central node")
```

```{r setup, include=TRUE}
G8<- subset(COM1, TimePoint!="1"&Clusterness=="1.13")
summary(lmp(SD~Distance+(1|Grid),data = G8))
```



```{r setup, include=TRUE}
G1_13<- subset(COM, TimePoint!="1"&Grid=="G1.13")
SD113D<- aov(SD~Distance,data = G1_13)
summary(SD113D)
ggline( G1_13,x= "Distance",y= "SD",
       add= c("mean_se","jitter"),
       ylab = "Shannon's diversity",xlab= "Distance from the central node")
```

```{r setup, include=TRUE}
G9<- subset(COM1, TimePoint!="1"&Clusterness=="1.18")
summary(lmp(SD~Distance+(1|Grid),data = G9))
```



```{r setup, include=TRUE}
G1_18<- subset(COM, TimePoint!="1"&Grid=="G1.18")
SD118D<- aov(SD~Distance,data = G1_18)
summary(SD118D)
ggline( G1_18,x= "Distance",y= "SD",
       add= c("mean_se","jitter"),
       ylab = "Shannon's diversity",xlab= "Distance from the central node")
```



```{r setup, include=TRUE}
G10<- subset(COM1, TimePoint!="1"&Clusterness=="1.29")
summary(lmp(SD~Distance+(1|Grid),data = G10))
```



```{r setup, include=TRUE}
G1_29<- subset(COM, TimePoint!="1"&Grid=="G1.29")
SD129D<- aov(SD~Distance,data = G1_29)
summary(SD129D)
ggline( G1_29,x= "Distance",y= "SD",
       add= c("mean_se","jitter"),
       ylab = "Shannon's diversity",xlab= "Distance from the central node")
```



##pearson correlation between diversity and distance at Grid0.6: -0.4842497
```{r setup, include=TRUE}
scatter.smooth(x=G0_6$Distance,y=G0_6$SD,main="G0.6Diversity~Distance")

cor(G0_6$Distance,G0_6$SD)

```
##pearson correlation between diversity and distance at Grid0.72: 0.05012
```{r setup, include=TRUE}
scatter.smooth(x=G0_72$Distance,y=G0_72$SD,main="G0.72Diversity~Distance")

cor(G0_72$Distance,G0_72$SD)

```


##pearson correlation between diversity and distance at Grid0.77: -0.1531
```{r setup, include=TRUE}
scatter.smooth(x=G0_77$Distance,y=G0_77$SD,main="G0.77Diversity~Distance")

cor(G0_77$Distance,G0_77$SD)

```

##pearson correlation between diversity and distance at Grid0.86: -0.4737925
```{r setup, include=TRUE}
scatter.smooth(x=G0_86$Distance,y=G0_86$SD,main="G0.86Diversity~Distance")

cor(G0_86$Distance,G0_86$SD)

```
##pearson correlation between diversity and distance at Grid0.92: -0.21755
```{r setup, include=TRUE}
scatter.smooth(x=G0_92$Distance,y=G0_92$SD,main="G0.92Diversity~Distance")

cor(G0_92$Distance,G0_92$SD)

```

##pearson correlation between diversity and distance at Grid1.02: -0.148559
```{r setup, include=TRUE}
scatter.smooth(x=G1_02$Distance,y=G1_02$SD,main="G1.02Diversity~Distance")

cor(G1_02$Distance,G1_02$SD)

```

##pearson correlation between diversity and distance at Grid1.09: -0.2612645
```{r setup, include=TRUE}
scatter.smooth(x=G1_09$Distance,y=G1_09$SD,main="G1.09Diversity~Distance")

cor(G1_09$Distance,G1_09$SD)

```

##pearson correlation between diversity and distance at Grid1.13: -0.2676533
```{r setup, include=TRUE}
scatter.smooth(x=G1_13$Distance,y=G1_13$SD,main="G1.13Diversity~Distance")

cor(G1_13$Distance,G1_13$SD)

```


##pearson correlation between diversity and distance at Grid1.18:-0.340112
```{r setup, include=TRUE}
scatter.smooth(x=G1_18$Distance,y=G1_18$SD,main="G1.18Diversity~Distance")

cor(G1_18$Distance,G1_18$SD)

```

##pearson correlation between diversity and distance at Grid1.29:-0.2788426
```{r setup, include=TRUE}
scatter.smooth(x=G1_29$Distance,y=G1_29$SD,main="G1.29Diversity~Distance")

cor(G1_29$Distance,G1_29$SD)

```

```{r setup, include=TRUE}
ggplot(CORDD,aes(x=Grid,y=corDD))+geom_point()+
  theme_classic()+
  labs(title="Coorelation value between shannon's diversity and Distance at each Grid")
```
