---
title: "Disperal gradient"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r,include=FALSE}
# Read libraries
library(tidyverse)
library(ggplot2)
library(readxl)
```

```{r,include=TRUE}
SPNETDISP <- read_excel("Desktop/SPATIAL NETWORK /SPATIONETWORK/SPNETDISP.xlsx")
#subset the data
SPNETDISP_BF<-subset(SPNETDISP,FncG=="BF") #Subset BF
SPNETDISP_G1<-subset(SPNETDISP,Grid=="R1.29")#SUBSET GRID 1.29
```


#plot per functional group grid1
```{r,echo=FALSE}
  ggplot(data= SPNETDISP_G1, mapping = aes(x= Time, y= Disp, color = FncG, group= FncG)) +
  labs(title ="Different functional group dispersal change with time in Grid 1.29 ", x ="Time points") +
 geom_point()+geom_line()+
theme_classic()
```


```{r,include=FALSE}
#subset the data
SPNETDISP_ROT<-subset(SPNETDISP,FncG=="ROT") #Subset ROT
SPNETDISP_FF<-subset(SPNETDISP,FncG=="FF") #Subset FF
SPNETDISP_PF<-subset(SPNETDISP,FncG=="PF") #Subset PF
SPNETDISP_PRE<-subset(SPNETDISP,FncG=="PRE") #Subset PRE
SPNETDISP_G2<-subset(SPNETDISP,Grid=="R1.18")#SUBSET GRID 1.18
SPNETDISP_G3<-subset(SPNETDISP,Grid=="R1.13")#SUBSET GRID 1.13
SPNETDISP_G4<-subset(SPNETDISP,Grid=="R1.09")#SUBSET GRID 1.09
SPNETDISP_G5<-subset(SPNETDISP,Grid=="R1.02")#SUBSET GRID 1.02
SPNETDISP_G6<-subset(SPNETDISP,Grid=="R0.92")#SUBSET GRID 0.92
SPNETDISP_G7<-subset(SPNETDISP,Grid=="R0.86")#SUBSET GRID 0.86
SPNETDISP_G8<-subset(SPNETDISP,Grid=="R0.77")#SUBSET GRID 0.77
SPNETDISP_G9<-subset(SPNETDISP,Grid=="R0.72")#SUBSET GRID 0.72
SPNETDISP_G10<-subset(SPNETDISP,Grid=="R0.6")#SUBSET GRID 0.6
```

#plot per functional group grid2

```{r,echo=FALSE}
  ggplot(data= SPNETDISP_G2, mapping = aes(x= Time, y= Disp, color = FncG, group= FncG)) +
   labs(title ="Different functional group dispersal change with time in Grid 1.18 ", x ="Time points") +
 geom_point()+geom_line()+
theme_classic()
```


#plot per functional group grid3
```{r,echo=FALSE}
  ggplot(data= SPNETDISP_G3, mapping = aes(x= Time, y= Disp, color = FncG, group= FncG)) +
   labs(title ="Different functional group dispersal change with time in Grid 1.13 ", x ="Time points") +
 geom_point()+geom_line()+
theme_classic()
```


#plot per functional group grid4
```{r,echo=FALSE}
  ggplot(data= SPNETDISP_G4, mapping = aes(x= Time, y= Disp, color = FncG, group= FncG)) +
   labs(title ="Different functional group dispersal change with time in Grid 1.09 ", x ="Time points") +
 geom_point()+geom_line()+
theme_classic()
```

#plot per functional group grid5
```{r,echo=FALSE}
  ggplot(data= SPNETDISP_G5, mapping = aes(x= Time, y= Disp, color = FncG, group= FncG)) +
   labs(title ="Different functional group dispersal change with time in Grid 1.02 ", x ="Time points") +
 geom_point()+geom_line()+
theme_classic()
```


#plot per functional group grid6
```{r,echo=FALSE}
  ggplot(data= SPNETDISP_G6, mapping = aes(x= Time, y= Disp, color = FncG, group= FncG)) +
   labs(title ="Different functional group dispersal change with time in Grid 0.92 ", x ="Time points") +
 geom_point()+geom_line()+
theme_classic()
```


#plot per functional group grid7
```{r,echo=FALSE}
  ggplot(data= SPNETDISP_G7, mapping = aes(x= Time, y= Disp, color = FncG, group= FncG)) +
   labs(title ="Different functional group dispersal change with time in Grid 0.86 ", x ="Time points") +
 geom_point()+geom_line()+
theme_classic()
```


#plot per functional group grid8
```{r,echo=FALSE}
  ggplot(data= SPNETDISP_G8, mapping = aes(x= Time, y= Disp, color = FncG, group= FncG)) +
   labs(title ="Different functional group dispersal change with time in Grid 0.77 ", x ="Time points") +
 geom_point()+geom_line()+
theme_classic()
```


#plot per functional group grid9
```{r,echo=FALSE}
  ggplot(data= SPNETDISP_G9, mapping = aes(x= Time, y= Disp, color = FncG, group= FncG)) +
   labs(title ="Different functional group dispersal change with time in Grid 0.72 ", x ="Time points") +
 geom_point()+geom_line()+
theme_classic()
```


#plot per functional group grid10
```{r,echo=FALSE}
  ggplot(data= SPNETDISP_G10, mapping = aes(x= Time, y= Disp, color = FncG, group= FncG)) +
   labs(title ="Different functional group dispersal change with time in Grid 0.6 ", x ="Time points") +
 geom_point()+geom_line()+
theme_classic()
```

#plot per Grid BF
```{r,echo=FALSE}
  ggplot(data= SPNETDISP_BF, mapping = aes(x= Time, y= Disp, color = Grid, group= Grid)) +
 geom_point()+geom_line()+
  labs(title ="Bacteria-feeder dispersal change between grids ", x ="Time points")+
theme_classic()
```


#plot per Grid ROTIFER
```{r,echo=FALSE}
  ggplot(data= SPNETDISP_ROT, mapping = aes(x= Time, y= Disp, color = Grid, group= Grid)) +
 geom_point()+geom_line()+
   labs(title ="Rotifer dispersal change between grids ", x ="Time points")+
theme_classic()
```


#plot per Grid FF
```{r,echo=FALSE}
  ggplot(data= SPNETDISP_FF, mapping = aes(x= Time, y= Disp, color = Grid, group= Grid)) +
 geom_point()+geom_line()+
   labs(title ="Fungi-feeder dispersal change between grids ", x ="Time points")+
theme_classic()
```


#plot per Grid PF
```{r,echo=FALSE}
  ggplot(data= SPNETDISP_PF, mapping = aes(x= Time, y= Disp, color = Grid, group= Grid)) +
 geom_point()+geom_line()+
   labs(title ="Plant-feeder dispersal change between grids ", x ="Time points")+
theme_classic()
```


#plot per Grid predator
```{r,echo=TRUE}
  ggplot(data= SPNETDISP_PRE, mapping = aes(x= Time, y= Disp, color = Grid, group= Grid)) +
 geom_point()+geom_line()+
   labs(title ="Predator dispersal change between grids ", x ="Time points")+
theme_classic()
```

