---
title: "Communitydata"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
library(readxl)
library(tidyverse)
library(ggplot2)
library(rcompanion) 
library(ggpubr)
library(dplyr)
library(car)
library(Rmisc)
library(lmPerm)
library(foreign)
library(MASS)
theme_set(theme_classic())
```


##Synchrony
#Permutation test
```{r setup, include=TRUE}
ggplot(CSS,aes(Grid,Synchrony))+
  geom_point()
```


#lmPerm: Exact argument for evaluate all permutations: synchrony~clusterness
```{r }
summary(lmp(Synchrony~Clusterness+(1|Grid),data = CSS1))
```

#synchrony ~distance
```{r setup, include=TRUE}
summary(lmp(Synchrony~Distance+(1|Grid),data = CSS1))
```

```{r setup, include=TRUE}
ggplot(CSS,aes(Distance,Synchrony))+
  geom_point()
```


#lmPerm: Prob argument to use the sequential probability  ratio to decidebetween two hypotheses about a p-value
```{r setup, include=TRUE}
summary(lmp(Synchrony~Grid,data = CSS,perm = "Prob"))
```

#ANOVA permutation analysis 
```{r setup, include=TRUE}
anova(lmp(Synchrony~Grid,data = CSS))
```


```{r setup, include=TRUE}
ggline(CSS1,x= "Clusterness",y= "Synchrony",palette = "red",
       add= c("mean_se","jitter"),point.color = "blue",
       ylab = "Synchrony",xlab= "Clusterness")
```






##COMMUNITY STABILITY
#Calculates the stability of the overall community over time as the temporal mean / temporal standard deviation of aggregate species abundances

#lmPerm: Exact argument for evaluate all permutations
```{r setup, include=TRUE}
summary(lmp(ComStab~Clusterness+(1|Grid),data = CSS1))
```



#lmPerm: Prob argument to use the sequential probability  ratio to decide between two hypotheses about a p-value
```{r setup, include=TRUE}
summary(lmp(ComStab~Clusterness+(1|Grid),data = CSS1,perm = "Prob"))
```

```{r setup, include=TRUE}
summary(lmp(ComStab~Distance+(1|Grid),data = CSS1))
```

#ANOVA permutation analysis 
```{r setup, include=TRUE}
anova(lmp(ComStab~Grid,data = CSS))
```

```{r setup, include=TRUE}
ggplot(CSS,aes(Grid,ComStab))+
  geom_boxplot()
```
```{r setup, include=TRUE}
ggplot(CSS,aes(Distance,ComStab))+
  geom_point()
```

##Distance include in each grid
```{r setup, include=TRUE}
CSS_06<-subset(CSS1,Grid=="G0.6")
CSS_072<-subset(CSS1,Grid=="G0.72")
CSS_077<-subset(CSS1,Grid=="G0.77")
CSS_086<-subset(CSS1,Grid=="G0.86")
CSS_092<-subset(CSS1,Grid=="G0.92")
CSS_102<-subset(CSS1,Grid=="G1.02")
CSS_109<-subset(CSS1,Grid=="G1.09")
CSS_113<-subset(CSS1,Grid=="G1.13")
CSS_118<-subset(CSS1,Grid=="G1.18")
CSS_129<-subset(CSS1,Grid=="G1.29")
CSS_C<- subset(CSS1, Location=="L4030")
```



## how synchrony change in each grid at different distance
```{r setup, include=TRUE}
ggplot(data = CSS_06,aes(Distance,Synchrony) )+geom_point()+
  theme_classic()+labs(title="Grid0.6")
ggplot(data = CSS_072,aes(Distance,Synchrony) )+geom_point()+
  theme_classic()+labs(title="Grid0.72")
ggplot(data = CSS_077,aes(Distance,Synchrony) )+geom_point()+
  theme_classic()+labs(title="Grid0.77")
ggplot(data = CSS_086,aes(Distance,Synchrony) )+geom_point()+
  theme_classic()+labs(title="Grid0.86")
ggplot(data = CSS_092,aes(Distance,Synchrony) )+geom_point()+
  theme_classic()+labs(title="Grid0.92")
ggplot(data = CSS_102,aes(Distance,Synchrony) )+geom_point()+
  theme_classic()+labs(title="Grid1.02")
ggplot(data = CSS_109,aes(Distance,Synchrony) )+geom_point()+
  theme_classic()+labs(title="Grid1.09")
ggplot(data = CSS_113,aes(Distance,Synchrony) )+geom_point()+
  theme_classic()+labs(title="Grid1.13")
ggplot(data = CSS_118,aes(Distance,Synchrony) )+geom_point()+
  theme_classic()+labs(title="Grid1.18")
ggplot(data = CSS_129,aes(Distance,Synchrony) )+geom_point()+
  theme_classic()+labs(title="Grid1.29")
```

## how community stability change in each grid at different distance
```{r setup, include=TRUE}
ggplot(data = CSS_06,aes(Distance,ComStab) )+geom_point()+
  theme_classic()+labs(title="Grid0.6")
ggplot(data = CSS_072,aes(Distance,ComStab) )+geom_point()+
  theme_classic()+labs(title="Grid0.72")
ggplot(data = CSS_077,aes(Distance,ComStab) )+geom_point()+
  theme_classic()+labs(title="Grid0.77")
ggplot(data = CSS_086,aes(Distance,ComStab) )+geom_point()+
  theme_classic()+labs(title="Grid0.86")
ggplot(data = CSS_092,aes(Distance,ComStab) )+geom_point()+
  theme_classic()+labs(title="Grid0.92")
ggplot(data = CSS_102,aes(Distance,ComStab) )+geom_point()+
  theme_classic()+labs(title="Grid1.02")
ggplot(data = CSS_109,aes(Distance,ComStab) )+geom_point()+
  theme_classic()+labs(title="Grid1.09")
ggplot(data = CSS_113,aes(Distance,ComStab) )+geom_point()+
  theme_classic()+labs(title="Grid1.13")
ggplot(data = CSS_118,aes(Distance,ComStab) )+geom_point()+
  theme_classic()+labs(title="Grid1.18")
ggplot(data = CSS_129,aes(Distance,ComStab) )+geom_point()+
  theme_classic()+labs(title="Grid1.29")
```




#Central node synchrony and community stability
```{r setup, include=TRUE}
ggplot(data = CSS_C,aes(Grid,Synchrony) )+geom_point()+
  theme_classic()+labs(title="Synchrony of central nodes in each grid")

ggplot(data = CSS_C,aes(Grid,ComStab) )+geom_point()+
  theme_classic()+labs(title="Community stability of central nodes in each grid")
```


#linear regression model:Synchrony~Grid central nodes

```{r setup, include=TRUE}
summary(lmp(Synchrony~Clusterness+(1|Grid),data = CSS_C))
MCS<- lm(Synchrony~Clusterness,data = CSS_C)
summary(MCS)

summary(lmp(ComStab~Clusterness+(1|Grid),data = CSS_C))
```
```{r setup, include=TRUE}
lm(Synchrony~Clusterness,data = CSS_C)
plot(Synchrony~Clusterness,data = CSS_C)
  abline(1.0521,-0.2821)
```

##Simple linear regression
#Each grid synchrony~distance
#Pearson coorelation
#Grid0.6-correlation=-0.19;GRID0.72=-0.375;GRID0.77=-0.267
```{r setup, include=TRUE}
scatter.smooth(x=CSS_077$Distance,y=CSS_077$Synchrony,main="Synchrony~Distance")
cor(CSS_077$Distance,CSS_077$Synchrony)
```

#Grid0.86-correlation=0.8528
```{r setup, include=TRUE}
scatter.smooth(x=CSS_086$Distance,y=CSS_086$Synchrony,main="Synchrony~Distance")
cor(CSS_086$Distance,CSS_086$Synchrony)# A strong relationship between grids and synchrony for GRID0.86 
```

#Grid1.02-correlation=0.635
```{r setup, include=TRUE}
scatter.smooth(x=CSS_102$Distance,y=CSS_102$Synchrony,main="Synchrony~Distance")
cor(CSS_102$Distance,CSS_102$Synchrony)
```

#Grid1.09-correlation=0.4879
```{r setup, include=TRUE}
scatter.smooth(x=CSS_109$Distance,y=CSS_109$Synchrony,main="Synchrony~Distance")
cor(CSS_109$Distance,CSS_109$Synchrony)
```

#Grid1.13-correlation=0.2559
```{r setup, include=TRUE}
scatter.smooth(x=CSS_113$Distance,y=CSS_113$Synchrony,main="Synchrony~Distance")
cor(CSS_113$Distance,CSS_113$Synchrony)
```

#Grid1.18-correlation=0.3196
```{r setup, include=TRUE}
scatter.smooth(x=CSS_118$Distance,y=CSS_118$Synchrony,main="Synchrony~Distance")
cor(CSS_118$Distance,CSS_118$Synchrony)
```

#Grid1.29-correlation=0.6163
```{r setup, include=TRUE}
scatter.smooth(x=CSS_129$Distance,y=CSS_129$Synchrony,main="Synchrony~Distance")
cor(CSS_129$Distance,CSS_129$Synchrony)
```

##linear regression model:Synchrony~distance
```{r setup, include=TRUE}
MOSD<- lm(Synchrony~Distance,data = CSS)
summary(MOSD)
Anova(MOSD,type = "II")
```

#linear regression model per grid:Synchrony~distance
```{r setup, include=TRUE}
MOSD1<- lm(Synchrony~Distance,data = CSS_06)
summary(MOSD1)
Anova(MOSD1,type = "II")
MOSD2<- lm(Synchrony~Distance,data = CSS_072)
summary(MOSD2)
Anova(MOSD2,type = "II")
MOSD3<- lm(Synchrony~Distance,data = CSS_077)
summary(MOSD3)
Anova(MOSD3,type = "II")
MOSD5<- lm(Synchrony~Distance,data = CSS_092)
summary(MOSD5)
Anova(MOSD5,type = "II")
```

#linear regression:Synchrony~distance,distance showed its significant effect on synchrony only in grid0.86, some weak distabnce effect on synchrony in grid1.02 and grid 1.29
```{r setup, include=TRUE}
MOSD4<- lm(Synchrony~Distance,data = CSS_086)
summary(MOSD4)
Anova(MOSD4,type = "II")

MOSD6<- lm(Synchrony~Distance,data = CSS_102)
summary(MOSD6)
Anova(MOSD6,type = "II")

MOSD10<- lm(Synchrony~Distance,data = CSS_129)
summary(MOSD10)
Anova(MOSD10,type = "II")
```


##linear regression model:Synchrony~GRID
```{r setup, include=TRUE}
MOSG<- lm(Synchrony~Grid,data = CSS)
summary(MOSG)
Anova(MOSG,type = "II")
```




#linear regression model:Community stability~grid
```{r setup, include=TRUE}
MOCG<- lm(ComStab~Grid,data = CSS)
summary(MOCG)
Anova(MOCG,type = "II")
```


#linear regression model:Community stability~DISTANCE
```{r setup, include=TRUE}
MOCD<- lm(ComStab~Distance,data = CSS)
summary(MOCD)
Anova(MOCD,type = "II")
```


#Each grid stability~distance
#Pearson coorelation
#Grid0.6-correlation=-0.3878;GRID0.72=0.385;GRID0.77=0.036
```{r setup, include=TRUE}
scatter.smooth(x=CSS_077$Distance,y=CSS_077$ComStab,main="ComStab~Distance")
cor(CSS_077$Distance,CSS_077$ComStab)
```

#Grid0.86-correlation=-0.7613617
```{r setup, include=TRUE}
scatter.smooth(x=CSS_086$Distance,y=CSS_086$ComStab,main="ComStab~Distance")
cor(CSS_086$Distance,CSS_086$ComStab)
```

#Grid1.02-correlation=0.2667
```{r setup, include=TRUE}
scatter.smooth(x=CSS_102$Distance,y=CSS_102$ComStab,main="ComStab~Distance")
cor(CSS_102$Distance,CSS_102$ComStab)
```

#Grid1.09-correlation=-0.27
```{r setup, include=TRUE}
scatter.smooth(x=CSS_109$Distance,y=CSS_109$ComStab,main="ComStab~Distance")
cor(CSS_109$Distance,CSS_109$ComStab)
```

#Grid1.13-correlation=-0.11828
```{r setup, include=TRUE}
scatter.smooth(x=CSS_113$Distance,y=CSS_113$ComStab,main="ComStab~Distance")
cor(CSS_113$Distance,CSS_113$ComStab)
```

#Grid1.18-correlation=0.1994
```{r setup, include=TRUE}
scatter.smooth(x=CSS_118$Distance,y=CSS_118$ComStab,main="ComStab~Distance")
cor(CSS_118$Distance,CSS_118$ComStab)
```

#Grid1.29-correlation=-0.563
```{r setup, include=TRUE}
scatter.smooth(x=CSS_129$Distance,y=CSS_129$ComStab,main="ComStab~Distance")
cor(CSS_129$Distance,CSS_129$ComStab)
```



#linear regression model per grid:ComStab~distance
```{r setup, include=TRUE}
MOCD1<- lm(ComStab~Distance,data = CSS_06)
summary(MOCD1)
Anova(MOCD1,type = "II")
MOCD2<- lm(ComStab~Distance,data = CSS_072)
summary(MOCD2)
Anova(MOCD2,type = "II")
MOCD3<- lm(ComStab~Distance,data = CSS_077)
summary(MOCD3)
Anova(MOCD3,type = "II")
MOCD5<- lm(ComStab~Distance,data = CSS_092)
summary(MOCD5)
Anova(MOCD5,type = "II")
```

#linear regression:community stability~distance,distance showed its significant effect on synchrony only in grid0.86
```{r setup, include=TRUE}
MOCD4<- lm(ComStab~Distance,data = CSS_086)
summary(MOCD4)
Anova(MOCD4,type = "II")

MOCD6<- lm(ComStab~Distance,data = CSS_102)
summary(MOCD6)
Anova(MOCD6,type = "II")

MOCD10<- lm(ComStab~Distance,data = CSS_129)
summary(MOCD10)
Anova(MOCD10,type = "II")
```



```{r setup, include=TRUE}
ggplot(COR,aes(x=Grid,y=CorDT))+geom_point()+
  theme_classic()+
  labs(title="Coorelation value between shannon's diversity and time in each grid")
```















